Recognizing Strong Gravitational Lenses

### 2015-03-14 doc/Course_Paper/paper.tex
adding course paper doc

% %%%%%%%%% ABSTRACT
% \begin{abstract}
%    The ABSTRACT is to be in fully-justified italicized text, at the top
%    of the left-hand column, below the author and affiliation
%    information. Use the word ``Abstract'' as the title, in 12-point
%    Times, boldface type, centered relative to the column, initially
%    capitalized. The abstract is to be in 10-point, single-spaced type.
%    Leave two blank lines after the Abstract, then begin the main text.
%    Look at previous CVPR abstracts to get a feel for style and length.
% \end{abstract}

@@

\begin{figure*}[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/1.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/2.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/3.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
  \caption{Typical Space Warps duds. Insets indicate regions where volunteers typically
  clicked.}
  \label{fig:duds}
\end{figure*}

\begin{figure*}[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=figs/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
  \caption{Typical sims. Insets indicate the location of the lens in the
  image.}
  \label{fig:sims}
\end{figure*}

@@

We plan to train a classifier on this data using two different methods. First,
we will code our own convolutional net in python using theano. Second, we will
apply transfer learning techniques to train on a convolutional net galaxy
morphology classifier, which has graciously been made available to us by Ryan
Keisler and which achieved 7th place in the 2014 Galaxy Zoo Kaggle competition.
This classifier runs $96\times96$ images through 3 convolutional layers and 2
fully-connected layers and predicts a galaxy to have one of 37 enumerated
morphologies. We plan to train our classifier on top of the first
fully-connected layer, which has 500 neurons.

@@

% {\small
% \bibliographystyle{ieee}
% \bibliography{egbib}
% }

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
    The detection of strong gravitational lenses
\end{abstract}

@@

\begin{figure*}[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/1.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/2.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/3.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
  \caption{Typical Space Warps duds. Insets indicate regions where volunteers typically
  clicked.}
  \label{fig:duds}
\end{figure*}

\begin{figure*}[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=Figures/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
  \caption{Typical sims. Insets indicate the location of the lens in the
  image.}
  \label{fig:sims}
\end{figure*}

@@

We plan to train a classifier on this data using two different methods. First,
we will code our own convolutional net in python using \textsc{theano}. Second,
we will apply transfer learning techniques to train on a convolutional net
galaxy morphology classifier, which has graciously been made available to us by
Ryan Keisler and which achieved 7th place in the 2014 Galaxy Zoo Kaggle
competition.  This classifier runs $96\times96$ images through 3 convolutional
layers and 2 fully-connected layers and predicts a galaxy to have one of 37
enumerated morphologies. We plan to train our classifier on top of the first
fully-connected layer, which has 500 neurons.

%-------------------------------------------------------------------------
\section{Results}

% Not sure if we put anything here?

%-------------------------------------------------------------------------
\subsection{Convolution Neural Network}

% TODO: Insert figure for architecture

%-------------------------------------------------------------------------
\subsection{Transfer Learning}

% TODO: Touch up description
\begin{figure}%[!ht]
\centering
\epsfig{file=Figures/architecture.pdf,width=\linewidth,angle=0,clip=}
\caption{Architecture of the convolution
  neural network trained on the galaxy zoo morphologies. The feature vector we
use comes from the fully connected layer.}
\label{fig:architecture}
\end{figure}

% TODO: Redescribe the network, including data augmentation and such.

%-------------------------------------------------------------------------
\section{Discussion}

% TODO: Remake with linear classifiers.
% TODO: Include results from CNN as well.
% TODO: Touch up description
\begin{figure}%[!ht]
\centering
\epsfig{file=Figures/roc_curve.pdf,width=\linewidth,angle=0,clip=}
\caption{Receiver Operating Curves for the Random
  Forest Transfer Learning and the \textsc{Space Warps} systems, divided by
  stage.}
  \label{fig:roc}
\end{figure}

%-------------------------------------------------------------------------
\section{Conclusions}

% Discuss how well things went. Or didn't go.

%-------------------------------------------------------------------------
\section{Acknowledgements}
We received access to the dataset through Phil Marshall
(\url{pjm@slac.stanford.edu}), who also graciously explained to us how
\textsc{Space Warps}
currently works. The convolutional neural network upon which the transfer
learning is based was kindly provided to us by Ryan Keisler
(\url{rkeisler@stanford.edu}).
All errors in interpretation or otherwise are entirely our own.

@@

% TODO: copy relevant bib stuff over so I don't have a 4 mb bib
{\small
\bibliographystyle{ieee}
\bibliography{coursebib}
}
